### 2017-09-09 paper/evaluation.tex

We ran the test suite for each subject three times, reporting averaged
execution times in three ranges: tests that run within a minute
(\shortg{}), tests that run in one to five minutes (\medg{}), and
tests that run in five or more minutes (\longg{}). Figure~\ref{fig:rq1-barplot} shows the number of projects in
each group.  As expected, \longg{} and \medg{} projects do not occur
as frequently as \shortg{} projects.  However, they do occur in
relatively high numbers.
Figure~\ref{fig:rq1-boxplot} shows the distribution of execution time of
test suites in each of these groups.
Note that the y-ranges are different.
The distribution associated with the \shortg{} group is the most
unbalanced (right skewed)\Comment{ with outliers closed to the \medg{}
group}.
The test suites in this group ran in 15 or less seconds for
over 75\% of the cases.\Comment{  Such scenarios constitute the majority of the
cases we analyzed.} Considering the groups \medg{} and \longg{},
however, we found many costly executions.  Nearly 75\% of the projects
from the \medg{} group take 3.5 or more minutes to run and nearly 75\% of
the projects from the \longg{} group take $\sim$20 minutes to run.  We
found cases in the \longg{} group were execution takes over 50 minutes
to complete, as can be observed from the outliers in the boxplot.

@@

Section~\ref{sec:rqA} showed that medium and long-running projects are
not uncommon, accounting to nearly \percentMedLongRunning{} of the
\numSubjs{} projects we analyzed.  Research question \numRQFeasibilityTwo{}
measures the distribution of test costs in test suites as to estimate
potential of obtaining speedups with parallelization.  In
the limit, if cost is dominated by a single test from a large test
suite, it is unlikely that parallelization will be beneficial as a
test method is the smallest working unit in test frameworks.
%% However, avoiding
%% frequent context switches is another factor to consider.  For example,
%% assuming there are at least two CPUs available for execution, cost can
%% be cut in half if two tests in a large test suite dominate execution
%% time and these tests are assigned to different CPUs.
%% It is therefore important to
%% speedup regressing testing in open-source projects.\Comment{not only
%%   to huge projects as those from Google~\cite{google-tap,google-ci}
%%   and Microsoft~\cite{prasad-shulte-ieee-microsoft-ci}.}
%% For the case
%% where cost is distributed more evenly across test cases, one expects
%% that speedups will be a function of the number of cores.
%% These contradictory forces, pushing number of tests and cost
%% of each test up and down, make prediction of effectiveness challenging.
Figure~\ref{fig:time-distributions} shows the time distribution of
individual test cases per project (x-axis denote projects appearing in
arbitrary order).
We observed that the average median value of execution cost for a
test was relatively small (dashed horizontal red lines), namely 0.08s
for \medg{} projects and 0.16s for \longg{} projects.
The standard deviations associated with each distribution were
relatively low.\Comment{ Figure~\ref{fig:sd} shows the number of
projects within specific ranges of $\sigma$ values.}  We noted a small
number of cases of CPU monopolization.

\begin{figure}[t!]
  \centering
  \includegraphics[width=.48\textwidth]{results/testcost-distribution.pdf}
  \caption{\label{fig:time-distributions}Time distributions per projects.}%
  \vspace{-3ex}
\end{figure}

For example, the highest value of $\sigma$ occurred in
\CodeIn{uber\_chaperone}, a project from the \longg{} group.
This project contains only 26 tests, 17 of which take less than 0.5s
to run, one of which takes nearly 3s to run, two of which take nearly
11s to run, four of which takes on average 3m to run, and two of which
take $\sim$8m to run.
For this project, 98.4\% of the execution cost is dominated by 20\% of
the tests; without these two costly tests this project would have been
classified as short-running.
We did not find other projects with such extreme time monopolization
profile.
Project \CodeIn{facebookarchive\_linkbench} is also classified as
long-running and has the second highest value of $\sigma$.
For this project, however, cost is distributed more smoothly across 98
tests, of which 8 (8.1\%) take more than 1s to run with the rest of
the tests running faster.
Figure~\ref{fig:time-distributions} shows that the average median
times are similar for \medg{} and \longg{}-running test suites.
The difference in overall running times is mainly justified by the
number of test cases as opposed to the individual costs of test cases.

Figure~\ref{fig:size-testsuites} shows the difference in the
distribution of test suite sizes across groups.  This figure indicates
that long projects, have a higher median and much higher average
number of test cases.
Furthermore, we noted a strong positive correlation between running
time and number of test on projects in the \longg{} group.
Considering the \medg{} group, the correlation between these two
variables was weak.
Figure~\ref{fig:scattercost} illustrates this regression line.

\begin{center}
\fbox{
\begin{minipage}{8cm}
  \textit{Answering \numRQFeasibilityTwo{}:}~\emph{Overall, results indicate that
  projects with a very small number of tests monopolizing end-to-end
  execution time were rare. Time most often is distribuited evenly
  across test cases.}
\end{minipage}
}
\begin{figure}[h!]
  \centering
  \begin{subfigure}{0.13\textwidth}
    \centering
    \includegraphics[width=.9\textwidth]{results/boxplots-testcases.pdf}
    \caption{\label{fig:size-testsuites}}
  \end{subfigure}
  \hfill
  \begin{subfigure}{0.28\textwidth}
    \centering
    \includegraphics[width=.9\textwidth]{results/scatter-testcost.pdf}
    \caption{\label{fig:scattercost}}
  \end{subfigure}
  \caption{\label{fig:time-versus-size}(a) Size of test suites; (b)
    Size versus running time of test suites.}%
\end{figure}
\end{center}

@@

  in old versions of Maven Surefire} to define the number of forked

>>>>

We ran the test suite for each subject three times, reporting averaged
execution times in three ranges: tests that run within a minute
(\shortg{}), tests that run in one to five minutes (\medg{}), and
tests that run in five or more minutes (\longg{}). Figure~\ref{fig:rq1-barplot} shows the number of projects in
each group.  As expected, \longg{} and \medg{} projects do not occur
as frequently as \shortg{} projects.  However, they do occur in
relatively high numbers.
Figure~\ref{fig:rq1-boxplot} shows the distribution of execution time of
test suites in each of these groups.
Note that the y-ranges are different.
The distribution associated with the \shortg{} group is the most
unbalanced (right skewed)\Comment{ with outliers closed to the \medg{}
group}.
The test suites in this group ran in 15 or less seconds for
over 75\% of the cases.\Comment{  Such scenarios constitute the majority of the
cases we analyzed.} Considering the groups \medg{} and \longg{},
however, we found many costly executions.  Nearly 75\% of the projects
from the \medg{} group take 3.5 or more minutes to run and nearly 75\% of
the projects from the \longg{} group take $\sim$20 minutes to run.  We
found cases in the \longg{} group were execution takes more than 50 minutes
to complete, as can be observed from the outliers in the boxplot.

@@

\begin{figure}[t!]
  \centering
  \includegraphics[width=.48\textwidth]{results/testcost-distribution.pdf}
  \caption{\label{fig:time-distributions}Distribution of test case time per project.}%
  \vspace{-3ex}
\end{figure}

Section~\ref{sec:rqA} showed that medium and long-running projects are
not uncommon, accounting to nearly \percentMedLongRunning{} of the
\numSubjs{} projects we analyzed.  Research question \numRQFeasibilityTwo{}
measures the distribution of test costs in test suites.\Comment{ as to estimate
potential of obtaining speedups with parallelization.}  In
the limit, if cost is dominated by a single test from a large test
suite, it is unlikely that parallelization will be beneficial as a
test method is the smallest working unit in test frameworks.
%% However, avoiding
%% frequent context switches is another factor to consider.  For example,
%% assuming there are at least two CPUs available for execution, cost can
%% be cut in half if two tests in a large test suite dominate execution
%% time and these tests are assigned to different CPUs.
%% It is therefore important to
%% speedup regressing testing in open-source projects.\Comment{not only
%%   to huge projects as those from Google~\cite{google-tap,google-ci}
%%   and Microsoft~\cite{prasad-shulte-ieee-microsoft-ci}.}
%% For the case
%% where cost is distributed more evenly across test cases, one expects
%% that speedups will be a function of the number of cores.
%% These contradictory forces, pushing number of tests and cost
%% of each test up and down, make prediction of effectiveness challenging.
Figure~\ref{fig:time-distributions} shows the time distribution of
individual test cases per project.
We observed that the average median times (see dashed horizontal red
lines) were small, namely 0.08s
for \medg{} projects and 0.16s for \longg{} projects, and the standard deviations associated with each distribution were
relatively low.\Comment{ Figure~\ref{fig:sd} shows the number of
  projects within specific ranges of $\sigma$ values.} High values of
$\sigma$ are indicative of CPU monopolization. We found only a small number
of those. The highest value of $\sigma$ occurred in
\CodeIn{uber\_chaperone}, a project from the \longg{} group.
This project contains only 26 tests, 17 of which take less than 0.5s
to run, one of which takes nearly 3s to run, two of which take nearly
11s to run, four of which takes on average 3m to run, and two of which
take $\sim$8m to run.
For this project, 98.4\% of the execution cost is dominated by 20\% of
the tests; without these two costly tests this project would have been
classified as short-running.
We did not find other projects with such extreme time monopolization
profile.
Project \CodeIn{facebookarchive\_linkbench} is also classified as
long-running and has the second highest value of $\sigma$.
For this project, however, cost is distributed more smoothly across 98
tests, of which 8 (8.1\%) take more than 1s to run with the rest of
the tests running faster.

Figure~\ref{fig:size-testsuites} shows the difference in the
distribution of test suite sizes across groups.  This figure indicates
that long projects have a higher median and much higher average
number of test cases.
Furthermore, we noted a strong positive correlation between running
time and number of test on projects in the \longg{} group.
Considering the \medg{} group, the correlation between these two
variables was weak.
Figure~\ref{fig:scattercost} illustrates the regression lines between
these the variables test suite cost and number of test cases.
To sum, we observed that for projects with long-running test suites
running time is typically
justified by the number of test cases as opposed to the cost of individual test cases.

%% Figure~\ref{fig:time-distributions} shows that the average median
%% times are similar for \medg{} and \longg{}-running test suites.

\begin{center}
\fbox{
\begin{minipage}{8cm}
  \textit{Answering \numRQFeasibilityTwo{}:}~\emph{Overall, results indicate that
  projects with a very small number of tests monopolizing end-to-end
  execution time were rare. Time most often is distribuited evenly
  across test cases.}
\end{minipage}
}
\begin{figure}[h!]
  \centering
  \begin{subfigure}{0.13\textwidth}
    \centering
    \includegraphics[width=.9\textwidth]{results/boxplots-testcases.pdf}
    \caption{\label{fig:size-testsuites}}
  \end{subfigure}
  \hspace{3ex}
  \begin{subfigure}{0.28\textwidth}
    \centering
    \includegraphics[width=.9\textwidth]{results/scatter-testcost.pdf}
    \caption{\label{fig:scattercost}}
  \end{subfigure}
  \caption{\label{fig:time-versus-size}(a) Size of test suites; (b)
    Size versus running time of test suites.}%
\end{figure}
\end{center}

@@

  in old versions of Maven Surefire.} to define the number of forked
